\chapter*{List of Publications \& Awards}
\begin{enumerate}
    \item Journal Articles
        \begin{enumerate}
            \item D’Aniello, Giuseppe, Massimo De Falco, and Nicola Mastrandrea. “Designing a Multi-Agent System Architecture for Managing Distributed Operations within Cloud Manufacturing.” Evolutionary Intelligence, April 1, 2020. \href{https://doi.org/10.1007/s12065-020-00390-z}{Link}
        \end{enumerate}
    \item Book Chapters
        \begin{enumerate}
            \item de Falco, Massimo, Nicola Mastrandrea, Wathiq Mansoor, and Luigi Rarità. “Situation Awareness and Environmental Factors: The EVO Oil Production.” In New Trends in Emerging Complex Real Life Problems, edited by Patrizia Daniele and Laura Scrimali, 1:209–17. AIRO Springer Series. Cham: Springer International Publishing, 2018. \href{https://doi.org/10.1007/978-3-030-00473-6_23}{Link}
        \end{enumerate}
    \item Conference Papers
        \begin{enumerate}
            \item de Falco, Massimo, Nicola Mastrandrea, and Luigi Rarità. “Integrating Capacity and Logistics of Large Additive Manufacturing Networks.” Procedia Manufacturing 39 (2019): 1421–27. \href{https://doi.org/10.1016/j.promfg.2020.01.310}{Link}
            \item de Falco, Massimo, Nicola Mastrandrea, and Luigi Rarità. “A Queueing Networks-Based Model for Supply Systems.” In Optimization and Decision Science: Methodologies and Applications, edited by Antonio Sforza and Claudio Sterle, 217:375–83. Springer Proceedings in Mathematics \& Statistics. Cham: Springer International Publishing, 2017. \href{https://doi.org/10.1007/978-3-319- 67308-0_38}{Link}
            \item Best Paper Award Winner: De Falco, Massimo, Luigi Rarità, and Abdallah Asan Alalawin. “Negotiating and Sharing Capacities of Large Additive Manufacturing Networks.” International Conference on Advances in Business, Management and Law (ICABML) 2017 1, no. 1 (December 24, 2017): 440–66. \href{https://doi.org/10.30585/icabml-cp.v1i1.37}{Link}
        \end{enumerate}
\end{enumerate}
